%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Simon Christian}{ Kr\"{u}ger}{Software engineer (iOS)} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Kistlerhofstraße 157
M\"{u}nchen, 81379 (Bavaria)
Germany
~
+49 (0) 170 88 78 345
\href{https://twitter.com/_cr0ss_}{@\_cr0ss\_}
~
\href{mailto:hallo@cr0ss.org}{hallo [at] cr0ss.org}
\href{https://cr0ss.org}{cr0ss.org}
%\href{http://facebook.com/johnsmith}{fb://jsmith}
\section{languages}
german mother tongue
english fluent conversation
\section{programming}
{\color{red} $\varheartsuit$} Swift,
Objective-C, Python,
CoreData, HealthKit
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\subsection{school}

\begin{entrylist}

%------------------------------------------------

\entry
{1997--2001}
{Primary School}
{G\"{u}tersloh}
{Grundschule Pavenst\"{a}dt}

%------------------------------------------------

\entry
{2001--2003}
{Trial degree (Erprobungsstufe)}
{G\"{u}tersloh}
{St\"{a}dtisches Gymnasium G\"{u}tersloh}

%------------------------------------------------

\entry
{2003--2008}
{General Certificate of Secondary Education (GCSE)}
{G\"{u}tersloh}
{Elly-Heuss-Knapp-Schule, St\"{a}dt. Realschule G\"{u}tersloh}

%------------------------------------------------

\entry
{2008--2011}
{Commercial high school, qualification for admission to a technical college}
{G\"{u}tersloh}
{Reinhard Mohn Berufskolleg, focus Math and Computer Science}

%------------------------------------------------

\end{entrylist}

\subsection{university}

\begin{entrylist}

%------------------------------------------------

\entry
{2011--2013}
{Bachelor of Science, Computer Science}
{Trier}
{Hochschule Trier, Trier University of Applied Science}

%------------------------------------------------

\entry
{2013--2014}
{Bachelor of Science, Computer Science - Secure and Mobile Systems}
{Trier}
{Hochschule Trier, Trier University of Applied Science}

%------------------------------------------------

\entry
{2015--today}
{Bachelor of Science, Business Administration and Computer Science}
{Bielefeld}
{Fachhochschule Bielefeld}

%------------------------------------------------
\\
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{internship}

\begin{entrylist}

%------------------------------------------------

\entry
{2010}
{Trainee - Development, Administration / Processing}
{G\"{u}tersloh}
{Medienfabrik G\"{u}tersloh GmbH, part of arvato: a Bertelsmann company}


\entry
{2010-2011}
{Trainee - Accounting and Controlling, Controlling / Strategy}
{Delbr\"{u}ck- Lippling}
{KaLa Autotechnik GmbH}

\entry
{2011}
{Trainee - Development, Administration / Processing}
{G\"{u}tersloh}
{Medienfabrik G\"{u}tersloh GmbH, part of arvato: a Bertelsmann company}

%------------------------------------------------

\end{entrylist}

\subsection{part time}

\begin{entrylist}

\entry
{2013--2014}
{Prosthetic Dentistry lab Kreber}
{Trier}
{Distribution}

%------------------------------------------------

\end{entrylist}

\subsection{self-employment}

\begin{entrylist}

\entry
{2015--today}
{Kayos UG (haftungsbeschr\"{a}nkt)}
{G\"{u}tersloh}
{Executive Director and Softwaredeveloper}

%------------------------------------------------
\\ 
\end{entrylist}

\subsection{employment}

\begin{entrylist}
	
	\entry
	{2017--today}
	{intive GmbH}
	{M\"{u}nchen}
	{Software Engineer (iOS)}
	
	%------------------------------------------------
	\\ 
\end{entrylist}

\newpage
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2013}
{Career service - etiquette in business}
{Certificate}
{Subject area: Dinner and Meeting}

%------------------------------------------------

\entry
{2014}
{Specialist for application development of software systems}
{Certificate}
{Hochschule Trier, Trier University of Applied Science}
%------------------------------------------------

\entry
{2017}
{Professional Scrum Master (PSM I)}
{Certificate}
{Scrum.org}
%------------------------------------------------
\\ 
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------

\section{projects}

\subsection{university}

\begin{entrylist}

%------------------------------------------------

\entry
{2013}
{AI Development for steering a sailboat}
{workshop}
{Supervisor: Prof. Dr.-Ing. Fritz Nikolai Rudolph}

%------------------------------------------------

\entry
{2014}
{Raspberry Pi enters a sailing regatta}
{teamproject}
{Supervisor: Prof. Dr.-Ing. Fritz Nikolai Rudolph}

%------------------------------------------------

\entry
{2014}
{My data belongs to me... - and Facebook bought WhatsApp!}
{scientific discipline}
{Supervisor: Prof. Kay M\"{a}rthesheimer \& Prof. Dr.-Ing. Fritz Nikolai Rudolph}

%------------------------------------------------

\entry
{2014}
{Cisco PIX 515 Firewall administration}
{internship IT-Security}
{Supervisor: Prof. Dr. Konstantin Knorr}

%------------------------------------------------

\entry
{2014}
{Dovecot Mailserver with ClamAV and Spamassassin}
{internship IT-Security}
{Supervisor: Prof. Dr. Konstantin Knorr}

%------------------------------------------------

\entry
{2014}
{Implementing an iOS Push-Service for WordPress}
{Applied Computer Science Project}
{Supervisor: Prof. Dr. Ernst Georg Haffner}

%------------------------------------------------

\entry
{2016}
{Inventory management System for the German Red Cross }
{Java / Database Project}
{Supervisor: Prof. Dr. Detlef Deßaules}

%------------------------------------------------

\end{entrylist}

\subsection{self-employment}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--2015}
{FSI - Fachschaft Informatik}
{Objective-C}
{Development and Release: Native iOS App with connection to an existing WordPress instance}

%------------------------------------------------

\entry
{2015}
{AdsDown Content Blocker}
{Swift2}
{Development and Release: Safari Content Blocker Extension for iOS}

%------------------------------------------------

\entry
{2015}
{caffe:ne}
{Swift2}
{Development and Release: Caffeine tracking Application with HealthKit}

%------------------------------------------------

\entry
{2015--today}
{PlugFinder - charging station finder}
{Swift3}
{Development and Upgrade: solely responsible for maintenance and evolution}

%------------------------------------------------
\\
\end{entrylist}

\subsection{employment}

\begin{entrylist}
	
	%------------------------------------------------
	
	\entry
	{2017}
	{unnamed project}
	{Objetive-C}
	{Security review - major german banking application}
	
	%------------------------------------------------
	
	\entry
	{2017}
	{unnamed project}
	{Swift3}
	{Concept and development - grocery delivery service consisting of three applications for the whole supply chain.}
	
	%------------------------------------------------
	
	\entry
	{2017-2018}
	{Esprit}
	{Swift}
	{Development and lead position - multi language e-commerce application}
	
	%------------------------------------------------
	\\
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{skills}

\begin{entrylist}

%------------------------------------------------

\entry
{Basic}
{PHP, CSS, Adobe Photoshop, Microsoft Windows (Server), Postfix, Apache2}
{}
%------------------------------------------------

\entry
{Intermediate}
{Python, Java, html, LaTeX, Git, Microsoft Office, Object-Oriented Programming}
{}
%------------------------------------------------

\entry
{Advanced}
{Objective-C, Swift, Network Administration, Multithreaded Applications}
{}
%------------------------------------------------

\entry
{iOS Dev}
{CoreData, HealthKit, AutoLayout, Client-Server Communication}
{}
%------------------------------------------------
\\
\end{entrylist}

\newpage
%----------------------------------------------------------------------------------------
%	commitment SECTION
%----------------------------------------------------------------------------------------

\section{commitment}

\begin{entrylist}

%------------------------------------------------

\entry
{2010--today}
{Voluntary member in registered society Crossnight e.V.}
{}
{Organisation and performance: events for alternative music and culture}

%------------------------------------------------

\entry
{2011--2013}
{Treasurer of the student association}
{}
{faculty of computer science, Hochschule Trier}

%------------------------------------------------

\entry
{2012--2014}
{Student member of the faculty council}
{}
{faculty of computer science, Hochschule Trier}

%------------------------------------------------

\entry
{2014--2016}
{IT-council, person in charge}
{}
{Westf\"{a}lischer Golf-Club G\"{u}tersloh e.V.}

%------------------------------------------------
\\
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
\textbf{professional:} software design, architecture, security, coffee making
\\
\textbf{personal:} bouldering, hiking, scuba-diving, sailing, literature, yoga

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

%\section{publications}

%\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

%\printbibsection{book}{books} % Print all books from the bibliography

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
%\end{refsection}

%\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
%\nocite{*}
%\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
%\end{refsection}

%\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

%\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}